\documentclass[11pt,twoside]{article}
\usepackage[compact=,paper=a4paper,largepaper=true,bibresource=manual.bib,hcenter=true]{ifiseries}
\newcommand{\emphasis}[1]{\emph{#1}}
\begin{document}
\title{Checklist Before Submitting to QA}
\date{}
\author{Kiel Computer Sciene Series (KCSS)}
\maketitle
\noindent
Please in particular check the following details before submitting your work for QA at the KCSS.
Should you have any questions, please consult the technical support as
pointed out on the \href{http://informatik.uni-kiel.de/kcss}{KCSS Home Page}.
\begin{enumerate}[label=(\arabic*)]
\item Is each paragraph correctly terminated?
  The end of a paragraph is indicated by \lstinline|\par|,
  or a blank line, or the start of a new chapter, section, etc.
  It is \emphasis{incorrect} to indicate the end of a paragraph by \lstinline|\\|,
  and this \emphasis{must not be done}, since \lstinline|\\| means a line break, and not the end of a paragraph.
\item Is there excessive vertical whitespace on some of the pages?
  If so, try to use \lstinline|\raggedbottom| at the beginning of the document.
  For individual pages, a fix is to use \lstinline|\par\vfill\pagebreak| at the end of the page.
\item Capitalization must be like this:
  \enquote{Please see Chapter 3 for details.}
  But: \enquote{In the next chapter, we will look at the details.}
\item If there is an ISBN on the cover or mentioned on the metadata page:
  is it really yours and the correct one?
  In particular, do not use a barcode of the ISSN
  and ensure that none of the example barcodes is used accidentally.
\item Is the DOI part of the bibliography entry on the metadata page?
\end{enumerate}
\end{document}
