\documentclass[11pt,oneside]{article}
\usepackage[compact=,paper=a4paper,largepaper=true,figure=,halfparskip,marginfrac=12]{ifiseries}

\begin{document}
\thispagestyle{empty}
\enlargethispage{2\baselineskip}
\selectlanguage{english}
\begin{center}
  \Large
  \textbf{Declaration of Consent}
  \normalsize
\end{center}
\medskip
\begin{tabular}[t]{@{}p{.5\textwidth}@{}p{.5\textwidth}@{}}
  Last Name: & First Name: \\[\baselineskip]
  Research Group (if applicable): \\[\baselineskip]
  Title of Work: \\[2\baselineskip]
  Author(s) of the Work: \\[\baselineskip]
  KCSS Number and Version: & Type (Diss.\@, Habil.\@, Other):
\end{tabular}
\par\bigskip
%
% begin UB
%
Hereby I irrevocably declare my consent
that the Department of Computer Science, Kiel University, referred to as \enquote{Department} in the following,
is allowed to make electronic copies of the work specified above
(including its book cover, all meta data, and the abstract),
referred to as \enquote{Work} in the following;
to make such copies available
(using also the meta data and the abstract, if available)
without charge
within the \enquote{Kiel Computer Science Series} (KCSS)
on the servers of the Department;
to convert the Work into other formats;
and to make all bibliographic data and the abstract
available to other data bases.
The Work will be electronically archived and published on the Internet
as long as this is technically possible at a reasonable cost.
Thus I grant the Department
the non-exclusive right to reproduce the Work on public data networks
and to transfer the Work on individual requests without charge.
\par
%
% end UB
%
Moreover I declare my consent
that users who download electronic copies of the Work
or who obtain electronic copies via other means
are allowed to create printed copies for their own use,
including the book cover.
The right and the possibility to do so is mentioned
on the websites of the Department.
\par
%
% begin UB
%
I declare that electronic publication of the Work by the Department
and production of printed copies by the users for their own use
will not infringe on the rights of other parties,
and that the Department and the users will be protected from any claims made by other parties.
%
% end UB
%
In particular, I declare that also in the future,
no rights of other parties will be infringed on
and that in particular the Work can be made available for download free of charge
by the Department also in the future,
even if the Work or parts of it are commercially used by me or others.
%
%
%
\par\medskip\small
Severability Clause:
If any term or provision of this declaration should be invalid or unenforceable
or should become invalid or unenforceable after signing the declaration,
the remaining terms and provisions of this declaration will remain in effect.
\normalsize\par\bigskip\bigskip\medskip
\begin{tabular}{@{}p{\textwidth/2}@{}p{\textwidth/2}@{}}
  Kiel, \rule{10em}{.3pt} & \hfill\rule{12em}{.3pt} \\
  & \hfill\begin{minipage}{12em}\centering(Signature)\end{minipage}
\end{tabular}
\end{document}
